---
title: "Instructed Eye movements"
output: 
  pdf_document:
  toc: true
  toc_depth: 2
fig_height: 2
fig_width: 6

---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(fig.width=6, fig.height=3) 
```

# Data overview 

This is to keep track of what everything means in the datasets as well as put all plots in one place to keep up to date. 

```{r load in the data}
load("scratch/Elle_switch_nar_data")

# round switch point
switch_df$switch_point <- as.numeric(switch_df$switch_point)
switch_df$switch_point <- round(switch_df$switch_point)

# show first few lines of data set
head(switch_df)
```

Part: For the second session this can be either 2 or 3. 2 is when there were no cues present, and 3 is when there were cues 

Separation: The separation of the two side boxes from the centre. Currently this is in pixels, but this can be changed

Fixated box: Says which box was fixated. 1 means the participant fixated the centre, 2 and 3 mean the side box was fixated.

Centre: This column was added to look at proportions of where participants looked. 1 means the centre was fixated, 0 means one of the side boxes was fixated.

# Plotting data
## Accuracy

The next few box plots show comparisons of accuracy between the conditions in both the first and second halves. For this, the first half for participants in the "Instructions" condition were being cued as to where to look.

The data were separated so as to be able to compare the two groups in both halves of the experiment.

``` {r separate datasets, include=FALSE}
# no instructions/first half 
no_inst_1 <- switch_df[switch_df$condition == "No_instructions" & 
                         switch_df$block < 5,]

# no instructions/second half 
no_inst_2 <- switch_df[switch_df$condition == "No_instructions" & 
                         switch_df$block > 4,]

# instructions/tutorial
inst_tut <- switch_df[switch_df$condition == "Instructions" & 
                        switch_df$part == 3,]

# instructions/task
inst_tas <- switch_df[switch_df$condition == "Instructions" & 
                        switch_df$part == 2,]

```

``` {r Make the plots, echo = FALSE}
# First half
fh_tut <- rbind(inst_tut, no_inst_1)

# set data for boxplts 
temp <- group_by(fh_tut,
                 participant,
                 condition)
ftut_box_dat <- summarise(temp,
                          correct = mean(correct))

# tidy 
rm(temp)

# get numbers for in text 
temp <- group_by(fh_tut, condition)
ftut_overall <- summarise(temp,
                          correct = mean(correct))

# make plots 
ftut_box_plt <- ggplot(ftut_box_dat, 
                       aes(condition, 
                           correct))
ftut_box_plt <- ftut_box_plt + geom_boxplot()
ftut_box_plt <- ftut_box_plt + ggtitle("First Half")


# display plots
ftut_box_plt
```

The average number of correct trials for the instructed group was `r round(ftut_overall$correct[ftut_overall$condition == "Instructions"], digits = 3)` and for the non-instructed group it was `r round(ftut_overall$correct[ftut_overall$condition == "No_instructions"], digits = 3)` 

``` {r show second half plot, echo = FALSE}
# Second half
sh_tas <- rbind(inst_tas, no_inst_2)

# set data for boxplts 
temp <- group_by(sh_tas,
                 participant,
                 condition)
stas_box_dat <- summarise(temp,
                          correct = mean(correct))

# tidy 
rm(temp)

# get numbers for in text 
temp <- group_by(sh_tas, condition)
stas_overall <- summarise(temp,
                          correct = mean(correct))

# make plots 
stas_box_plt <- ggplot(stas_box_dat, 
                       aes(condition, 
                           correct))
stas_box_plt <- stas_box_plt + geom_boxplot()
stas_box_plt <- stas_box_plt + ggtitle("Second Half")

# show plot
stas_box_plt
```

The average number of correct trials for the instructed group was `r round(stas_overall$correct[stas_overall$condition == "Instructions"], digits = 3)` and for the non-instructed group it was `r round(stas_overall$correct[stas_overall$condition == "No_instructions"], digits = 3)` 

## Fixation proportions
The same again is shown here, first half by both conditions and the same for the second half

``` {r make proportions plots for first half, fig.height = 7, fig.width = 7.5, echo = FALSE}
# centre proportions
temp <- group_by(fh_tut, participant,separation,condition)
centre_prop <- summarise(temp, prop_fixated = mean(centre))
centre_prop$box <- "centre"

# side proportions
side_prop <- summarise(temp, prop_fixated = 1 - mean(centre))
side_prop$box <- "side"

# tidy
rm(temp)

# merge data
plt_dat_fh <- rbind(centre_prop, side_prop)

# tidy 
rm(centre_prop, side_prop)

# add back in switch_points
temp <- group_by(fh_tut, participant, condition)
switch_points <- summarise(temp, switch_point = unique(switch_point))

# make plot 
# tidy 
rm(temp)

# now to make the plots 
prop_plt_fh <- ggplot(data = plt_dat_fh, 
                      aes(x = separation,
                          y = prop_fixated))
prop_plt_fh <- prop_plt_fh + geom_area(aes(colour = box,
                                           fill = box),
                                       position = "stack")
prop_plt_fh <- prop_plt_fh + geom_vline(data = switch_points,
                                        aes(xintercept = as.numeric(switch_point)), 
                                        linetype = "dashed")
prop_plt_fh <- prop_plt_fh + ggtitle("First Half")
prop_plt_fh <- prop_plt_fh + facet_wrap(~condition + participant)
prop_plt_fh
```

``` {r make proportions plots for second half, fig.height = 7, fig.width = 7.5, echo = FALSE}
# centre proportions
temp <- group_by(sh_tas, participant,separation,condition)
centre_prop <- summarise(temp, prop_fixated = mean(centre))
centre_prop$box <- "centre"

# side proportions
side_prop <- summarise(temp, prop_fixated = 1 - mean(centre))
side_prop$box <- "side"

# tidy
rm(temp)

# merge data
plt_dat_sh <- rbind(centre_prop, side_prop)

# tidy 
rm(centre_prop, side_prop)

# add back in switch_points
temp <- group_by(sh_tas, participant, condition)
switch_points <- summarise(temp, switch_point = unique(switch_point))

# make plot 
# tidy 
rm(temp)

# now to make the plots 
prop_plt_sh <- ggplot(data = plt_dat_sh, 
                      aes(x = separation,
                          y = prop_fixated))
prop_plt_sh <- prop_plt_sh + geom_area(aes(colour = box,
                                           fill = box),
                                       position = "stack")
prop_plt_sh <- prop_plt_sh + geom_vline(data = switch_points,
                                        aes(xintercept = as.numeric(switch_point)), 
                                        linetype = "dashed")
prop_plt_sh <- prop_plt_sh + ggtitle("Second Half")
prop_plt_sh <- prop_plt_sh + facet_wrap(~condition + participant)
prop_plt_sh
```

# Notes
Currently there is a discrepancy between my caluculations of participants' switching points and Josephine's in the data which means that (by my estimates) some participants only have 3 separations below the switch point and 5 above.

``` {r Final tidy, include = FALSE}
rm(list = ls())
```
